Large-scale harmonic patterns clustering

### 2010-03-20 Paper/Paper.tex
new draft improved
improved, almost all figures in

\section{Experiments}\label{sec:experiments}

\subsection{Basic Properties}
This section present some fundamental results of the clustering algorithm.
These are important, but do not change the larger picture. Thus we will not
spend too much time describing them. In short: more training samples is
better, more codes is better, larger patterns are more difficult.

First, a larger dataset gives a better encoding codebook. See Figure
\ref{fig unknown}.

Secondly, a larger codebook better encodes new song. See Figure \ref{ejdue}.

Finally, larger patterns are more difficult to encode, thus require
larger codebooks. See Figure \ref{mouahahah}.

@@

@@

\subsection{Encoding of a Song}
Here we present a song with its two encodings. First, the harmonic patterns
given by the EchoNest. Secondly, each pattern is encoded by its closest
code in the codebook. See Figure \ref{youppie}.

\subsection{Codebook}
We can present the most typical patterns (Figure \ref{1}). 
Then, LLE? (Figure \ref{2}). 
Then, the graph on variance. (Figure \ref{fig:code_var}).

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{codes_lle}
\end{center}
\caption{Locally linear embedding (LLE) visualization of the codebook.}
\label{fig:lle}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{code_variance}
\end{center}
\caption{Average variance in time of a codebook.}
\label{fig:code_var}
\end{figure}

\subsection{Cluster}
Here we present real patterns that are closer to the code presented in ...
than any other code. The goal is to feel how much variance is present in
a cluster.

\section{Further Experiments}

@@

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{conf_mat_per_artist}
\end{center}
\caption{Confusion matrix for artist recognition task.}
\label{fig:conf_mat}
\end{figure}

>>>>

\section{Experiments - Fundamentals}\label{sec:experiments}
Note that we will present two additional experiments in 
Section \ref{sec:exps2}.

\subsection{Basic Properties}
This section present some fundamental results of the clustering algorithm.
These are important, but do not change the larger picture. Thus we will not
spend too much time describing them. In short: more training samples is
better, more codes is better, larger patterns are more difficult.
\begin{itemize}
\item First, a larger dataset gives a better encoding codebook. See Figure
\ref{fig:data_sizes}.
\item Secondly, a larger codebook better encodes new song. See 
Table \ref{tab:cbsize}.
\item Finally, larger patterns are more difficult to encode, thus require
larger codebooks. See Figure \ref{fig:perbeat}.
\end{itemize}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.99\columnwidth]{data_sizes}
\end{center}
\caption{\small{Distortion for a codebook of size $100$ encoding one bar
at a time, a bar being represented by $4$ chroma feature vector.
Therefore, a code or a pattern is of size $12$ x $4$ = $48$.
Distortion measure on the test data set. Data size tested range
from $10$ thousands to $2$ millions. Patterns were selected at
random from the dataset of approximately $3,7$ million patterns.}}
\label{fig:data_sizes}
\end{figure}

% NEW RESULTS COMING SOON WITH FIXED SIZED DATASET
\begin{table}
\begin{center}
\begin{tabular}{|l|l|c|}
\hline
\# codes & \# samples & avg. dist \\ \hline \hline
1 & $500$ & $0.066079$ \\
10 & $5$K & $0.045690$ \\
50 & $25$K & $0.038456$ \\
100 & $50$K & $0.036725$ \\
200 & $100$K & $0.033923$ \\
500 & $250$K & $0.030973$ \\
1000 & $500$K & \\ \hline
\end{tabular}
\end{center}
\caption{\small{Experiment with the codebook size. We train on patterns
corresponding to $1$ bar resized to $4$ beats. The number of training
samples is set to $500$ times the number of codes, which is sufficient
according to Figure \ref{fig:sizes}. NEW RESULTS COMING SOON WITH FIXED 
SIZED DATASET }}
\label{tab:cbsize}
\end{table}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{encoding_per_beat}
\end{center}
\caption{\small{Encoding larger and larger patterns with a fixed size
codebook.}}
\label{fig:perbeat}
\end{figure}

@@

\subsection{Encoding of a Song}
Here we present a song with its two encodings. First, the harmonic patterns
given by the EchoNest. Secondly, each pattern is encoded by its closest
code in the codebook. See Figure \ref{fig:encodesong}.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{song_encoded}
\end{center}
\caption{\small{Original song and its encoding. Must get a better one for
the paper!!!!!!}}
\label{fig:encodesong}
\end{figure}

\subsection{Codebook}
We can present the most typical patterns (Figure \ref{fig:codes1}). 
Then, LLE? (Figure \ref{fig:lle}). 
Then, the graph on variance. (Figure \ref{fig:code_var}).

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{codes1}
\end{center}
\caption{\small{Most used codes in the codebook.}}
\label{fig:codes1}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{codes_lle}
\end{center}
\caption{\small{Locally linear embedding (LLE) visualization of the codebook.}}
\label{fig:lle}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{code_variance}
\end{center}
\caption{\small{Average variance in time of a codebook.}}
\label{fig:code_var}
\end{figure}

\subsection{Cluster}
Here we present real patterns that are closer to the code presented in ...
than any other code. The goal is to feel how much variance is present in
a cluster. See Figure \ref{fig:cluster}.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{close_patterns1}
\end{center}
\caption{\small{Cluster around some pattern... TO BE REDONE}}
\label{fig:cluster}
\end{figure}

\section{Further Experiments}\label{sec:exps2}

@@

See Table \ref{tab:offset}.

\begin{table}
\begin{center}
\begin{tabular}{c|c}
%\hline
offset & \% of times chosen \\ \hline
0 & $\mathbf{62.6}$\\
1 & $16.5$\\
2 & $09.4$\\
3 & $11.5$\\
\end{tabular}
\end{center}
\caption{\small{
Best offset according to our codebook. The real one is $0$.
}}
\label{tab:offset}
\end{table}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{conf_mat_per_artist}
\end{center}
\caption{\small{Confusion matrix for artist recognition task.}}
\label{fig:conf_mat}
\end{figure}

Looking at the most typical patterns per artist can be insightful.
To find these patters, we compare its use by one artist and divide
by its use by all artists. In Figure \ref{fig:metallica} we see 
Metallica's pattern and in Figure \ref{fig:amosvega}, Tori Amos and
Suzanne Vega's pattern. These three artists were easily identified.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.4\columnwidth]{metallica_pattern}
\end{center}
\caption{\small{Most typical pattern for Metallica.}}
\label{fig:metallica}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.4\columnwidth]{toriamos_suzannevega_pattern}
\end{center}
\caption{\small{Most typical pattern for Tori Amos and Suzanne Vega.}}
\label{fig:amosvega}
\end{figure}
